\documentclass[12pt, letterpaper]{article}

\title{Can \c Serif Mekik}
\date{}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\marg}{0.5in}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[usenames]{xcolor}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{enumitem}
\usepackage{longtable}
\setlist[itemize]{nosep}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%thankyou, http://tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell

\usepackage{multicol}

\newcommand{\specialcell}[3][c]{%
  \begin{tabular}[#1]{@{}#2@{}}#3\end{tabular}}

\definecolor{my-gray}{gray}{0.7}
\sethlcolor{my-gray}

\begin{document}
%\maketitle
\thispagestyle{empty}
\begin{center}
Curriculum Vitae\\
{\large Can \c Serif Mekik}\\
\today
\end{center}

\noindent Department of Cognitive Science\\
Rensselaer Polytechnic Institute\\
110 8th St, Troy, NY, USA 12180\\
\texttt{mekikc@rpi.edu}

\subsubsection*{EDUCATION}

\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2020 & PhD, Department of Cognitive Science, Rensselaer Polytechnic Institute.\\
2016 & M.\ Cog.\ Sc., Institute of Cognitive Science, Carleton University.\\
2014 & Hon.\ B.\ Sc. in Cognitive Science \& Mathematics, University of Toronto.
\end{longtable}

\subsubsection*{PUBLICATIONS}

\subsubsection*{Conference Papers}

\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2018 & \noindent\hangindent=1cm Mekik, C.; Sun, R.; and Dai, D.\ Y. Similarity-based and Rule-based Reasoning in Raven's Matrices. In I.\ Juvina, J.\ Houpt, and C.\ Myers (Eds.), \emph{Proceedings of the 16th International Conference on Cognitive Modeling} (ICCM-2018; pp.\ 76--82). Madison, WI: University of Wisconsin.\\

2018 & \noindent\hangindent=1cm Mekik, C.; Sun, R.; and Dai, D.\ Y. Similarity-Based Reasoning, Raven's Matrices, and General Intelligence. In Jérôme Lang (Ed.), \emph{Proceedings of the Twenty-Seventh International Joint Conference on Artificial Intelligence} (IJCAI-2018; 1576--1582).\\

2017 & \noindent\hangindent=1cm Mekik, C.; Sun, R.; and Dai, D.\ Y. Deep Learning of Raven's Matrices. In \emph{Proceedings of the Fifth Annual Conference on Advances in Cognitive Systems} (ACS-2017).
\end{longtable}

\subsubsection*{Other Publications}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2015&\noindent\hangindent=1cm Galang, M. \& Mekik, C. Existence versus primacy: A critical overview of phenomenal intentionality. \emph{Noesis: An Undergraduate Journal of Philosophy, 16}. University of Toronto.
\end{longtable}

\subsubsection*{HONORS AND AWARDS}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017 & 2nd Place Graduate Essay, 75th McKinney Writing Contest, Rensselaer Polytechnic Institute. \\
\end{longtable}

\subsubsection*{GRANTS AND FELLOWSHIPS}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017 & Humanities, Arts and Social Sciences Fellowship, Rensselaer Polytechnic Institute. \\
2015 & Hamlin Graduate Fellowship, Carleton University. \\
2014 & Departmental Scholarship, Institute of Cognitive Science, Carleton University.
\end{longtable}

\subsubsection*{CONFERENCE ACTIVITY}

\subsubsection*{Talks}

\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2016 & \noindent\hangindent=1cm Mekik, C. and Singh, R. \emph{Turkish disjunctions and the morphological realization of `exh'}. Disjunction Days, June 2--3, 2016, ZAS Berlin, Berlin, Germany.\\

2015 & \noindent\hangindent=1cm Mageau, M., Mekik, C. and Wang, E. \emph{Foreign accents in song and speech}. 2015 Ottawa Conference for Linguistics Undergraduates and Master's Students (OCLU+M 2015), December 5, 2015, University of Ottawa, Ottawa, ON. \\

2015 & \noindent\hangindent=1cm Mekik, C.\ S.\ \emph{Covert Exhaustification and Turkish Disjunctive Phrases}. 8th Annual Toronto-Ottawa-Montreal Workshop on Semantics (TOM-8), April 11, 2015, Carleton University, Ottawa, ON.
\end{longtable}

\subsubsection*{Posters}

\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2016 & \noindent\hangindent=1cm Mekik, C.\ and Vertolli, M. \emph{Towards computer implementations of exh}. MIT Workshop on Exhaustivity 2016, September 10, 2016, Massachussets Institute of Technology, Boston, MA.\\

2016 & \noindent\hangindent=1cm Mekik, C.\ and Vertolli, M. \emph{Towards computer implementations of exh}. 9th Annual Toronto-Ottawa-Montreal Workshop on Semantics (TOM-9), April 23, 2016, McGill University, Montréal, QC.\\

2015 & \noindent\hangindent=1cm Mekik, C.\ S., Somers, S., Vertolli, M.\ O., Davies, J., Stewart, T.\ C. \emph{Nimage: Using Visible Persistence to Constrain a Model of Visual Processing}. 25th Annual Meeting of the Canadian Society for Brain Behavior and Cognitive Science (CSBBCS-2015), June 5--7, 2015, Ottawa, ON. \\
\end{longtable}

\subsubsection*{DEPARTMENTAL TALKS}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017&\noindent\hangindent=1cm Mekik, C. \emph{A computational account of a general intelligence test: Synergy between artificial intelligence and psychometric testing.} Department of Cognitive Science, Rensselaer Polytechnic Institute, Troy, NY.\\

2017&\noindent\hangindent=1cm Mekik, C. \emph{A Deep Learning Model of Raven's Matrices: Promise and Progress.} Department of Cognitive Science, Rensselaer Polytechnic Institute, Troy, NY.\\

2016&\noindent\hangindent=1cm Mekik, C. \emph{Developing an Automated Evaluation Procedure for Artificial Imagination Systems.} Department of Cognitive Science, Rensselaer Polytechnic Institute, Troy, NY.\\

2016&\noindent\hangindent=1cm Mageau, M.\ \& Mekik, C. \emph{Foreign accents in song and speech.} Institute of Cognitive Science, Carleton University, Ottawa, ON.
\end{longtable}

\subsubsection*{TEACHING EXPERIENCE}

\subsubsection*{Rensselaer Polytechnic Institute}

\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017 & TA, Forensic Psychology.\\
2016 & TA, Psychology and the Law.
\end{longtable}

\subsubsection*{Carleton University}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2016 & TA, Introduction to Cognitive Science.\\
2015 & TA, Mysteries of the Mind.
\end{longtable}

\subsubsection*{RESEARCH EXPERIENCE}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017 & \noindent\hangindent=1cm RA for Ron Sun, Rensselaer Polytechnic Institute.\\
2015 & \noindent\hangindent=1cm RA for Raj Singh, Carleton University.
\end{longtable}

\subsubsection*{SERVICE TO PROFESSION}
\begin{longtable}{p{.05\textwidth}p{.9\textwidth}}
2017 & \noindent\hangindent=1cm Reviewer, \emph{Neural Networks}.
\end{longtable}

\subsubsection*{LANGUAGES}
\begin{tabular}{l}
Turkish (native)\\
English (native)\\
French (fluent)\\
German (basic)
\end{tabular}

\end{document}
